Our Title

### 2015-05-04 draft.tex
Added in correct reference for Executive Order 13526.

\subsection{??????? Add in Ref 10 below from Bushra  ???????}

The Information Security Oversight Office (ISOO) determines standards for information classification based on policy guidance from the National Security Council (NSC). ISOO has oversight of the extensive security characterization framework and the National Industrial Security Program. ISOO sets requirements for the original classification of information if the following apply: information should be classified by the classification authority; information is belongs to, controlled by, or is for the United States; information refers to one of the classification categories; classification authorities determines damage will be caused to national security from unsanctioned disclosure [10]. The classes of information classification believed to be effective \cite{Richelson2011}, [10].  The general classes of classification are:

10 Federal Register. "The President”, Part VII 75, 2010

@@

\subsection{??????? Add in Ref 10 below from Bushra  ???????}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral [11] and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt [10])                                                  \\ \hline
\end{tabular}
\caption{My caption}
\label{tab:relation_table}
\end{table}

>>>>

The Information Security Oversight Office (ISOO) determines standards for information classification based on policy guidance from the National Security Council (NSC). ISOO has oversight of the extensive security characterization framework and the National Industrial Security Program. ISOO sets requirements for the original classification of information if the following apply: information should be classified by the classification authority; information is belongs to, controlled by, or is for the United States; information refers to one of the classification categories; classification authorities determines damage will be caused to national security from unsanctioned disclosure \cite{Office2010}. The classes of information classification believed to be effective \cite{Richelson2011,Office2010}.  The general classes of classification are:

@@

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral [11] and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt \cite{Office2010})                                                  \\ \hline
\end{tabular}
\caption{My caption}
\label{tab:relation_table}
\end{table}
